Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-26 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily~\citep{HOSTunpublished}. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is indeed a QIVPM.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we introduce a few technical notions. We call a state~$\rho$
a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
but any pure state is not totally mixed. We also define a notion of
distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
and the set of all states whose distance with $\rho$ is bounded by
$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$.

Since we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
and estimate the states consistent with it by the following theorem.

@@

\noindent In another word, if a state~$\rho'$ is consistent with
$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, the difference between the
Born quantum probabilities on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
must be bounded by $1/n$ which is the maximal length of the intervals
in $\mathscr{I}_{n}$. So does the distance between $\rho$ and $\rho'$,
$\left\Vert \rho-\rho'\right\Vert $. Conversely, if the distance
between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$, so does
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$.
Since the dimension of the Hilbert space is $3$, the same difference
on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
is bounded by $\frac{1}{4n}$. Moreover, the interiors of the intervals
in $\mathscr{I}_{n}$ shrinks $\frac{0.5}{2n}$ from the both ends,
excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$, $\left[\tfrac{2n-1}{2n},1\right]$,
and $\necess$. Together with the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$
and $0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ are both in the same
intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.

As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the state very close to
$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.

>>>>

\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is indeed a QIVPM.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we introduce a few technical notions. We call a state~$\rho$
a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
but any pure state is not totally mixed. We also define a notion of
distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
and the set of all states whose distance with $\rho$ is bounded by
$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
By expending the definitions, we have $\rho'\in B_{\epsilon}\left(\rho\right)$
if and only if $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\epsilon$
for any pure state~$\ket{\psi}$. This fact will be used to prove
the following theorem that is obtained by replacing the QIVPM~$\bar{\mu}$
in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
and estimate the states consistent with it.

@@

\noindent On the one hand, if a state~$\rho'$ is consistent with
$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, the difference between the
Born quantum probabilities on any 1-dimensioal projector~$\proj{\psi}$,
$\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
must be bounded by $1/n$ which is the maximal length of the intervals
in $\mathscr{I}_{n}$, i.e., $\rho'\in B_{1/n}\left(\rho\right)$.
On the other hand, if $\rho'\in B_{\frac{1}{12n}}\left(\rho\right)$,
we have $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\le\frac{1}{12n}$
for any pure state~$\ket{\psi}$. Since the dimension of the Hilbert
space is $3$, the same difference on any projector~$P$, $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|$,
is bounded by $\frac{1}{4n}$. Moreover, the interiors of the intervals
in $\mathscr{I}_{n}$ shrinks $\frac{0.5}{2n}$ from the both ends,
excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$, $\left[\tfrac{2n-1}{2n},1\right]$,
and $\necess$. Together with the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$
and $0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ must both be in the
same intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.

As a concrete example of Thm.~\ref{thm:Finite-precision-Gleason},
since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$
that should imply $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the state very close to
$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.
